The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
Finished new RQ1 Draft

\smallskip \noindent
\textbf{Updative  }
%Define
Updative changes are defined to be changes to documentation and are not changes that affect functionality in any way.

\smallskip \noindent
\textbf{Reformative  }
%Define
Reformative changes are defined to be changes that update the documentation to the stakeholders needs.

\smallskip \noindent
\textbf{Evaluative, Consultive and Training  }
%Define
Blabla...

>>>>

\smallskip \noindent
\textbf{Updative  }
%Define
Updative changes are defined to be changes to documentation and are not changes that affect functionality in any way. We also considered updates to example code and other training material to be Updative types of change.
%Data and example
A single change was determined to be Updative. This change was the updating of the API documentation to match the new API. The updates included a new API specification, deprecation list and the inclusion of the new features and libraries.
%Conclusion
Updative changes have very little impact on the functionality of the API yet they are still important changes for the usability of the API \cite{shi2011empirical}. We therefore conclude that the evolution of an API is not driven by updative changes.

\smallskip \noindent
\textbf{Reformative  }
%Define
Reformative changes are defined to be changes that update the documentation to the stakeholders needs.
%Data and Example
One reformative change was identified between version 1.4 and version 2.0 which involved a re-write of the existing example programs. The aim of the re-write was to update the examples to take advantage of the new functionality in the API while simultaneously showing how the modules interact and presenting a standard for how to use the API correctly.
%Conclusion
The reformative change that was found indicates therefore that updating documentation and example code is to some extent import for API evolution.

\smallskip \noindent
\textbf{Evaluative, Consultive and Training  }
%Define
Evaluative, Consultive and Training are all types of activities, rather than changes that a system can undergo. Evaluative activities are defined as activities such as auditing or evaluating the software. Similarly, consultive activities involve consultations with customers about the software. Finally, Training activities involve training for customers and users of the software.
%Data and example
None of the aforementioned activities occurred as part of the APIs evolution as these activities do not play a role in API evolution. This is supported by the fact none of the activities were identified for the changes.
%Conclusion
We can therefore conclude that these change types are not important for API evolution.
